### 2012-06-15 inst/examples/value_of_information.Rmd
summary stats

``` {r cache=FALSE}
base <- simulatereps(det, 0, 0, 0)
reckless <- simulatereps(det, .2, .2, .2)
````

``` {r cache=FALSE}
full <- simulatereps(gmi, .2, .2, .2)
cautious <- simulatereps(gmi, 0, 0, 0)
````

``` {r tidy, cache=FALSE}
sims <- list(base = base$sims, full = full$sims, reckless=reckless$sims, cautious=cautious$sims)
dat <- melt(sims, id=names(sims[[1]][[1]]))  
dt <- data.table(dat)
setnames(dt, c("L2", "L1"), c("reps", "uncertainty")) # names are nice
````

@@

``` {r  onerep, cache=FALSE }
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, fishstock)) +
  geom_line(aes(time, harvest), col="darkgreen") + 
  facet_wrap(~uncertainty) 
````

@@

``` {r  fig.cap="the induced dynamics in the stock size over time, for all replicates, by scenario", cache=FALSE}
p1 <- ggplot(dt) 
p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1) + facet_wrap(~uncertainty)
````

``` {r fig.cap="The profits made in each time interval of a single replicate, by scenario", cache=FALSE}
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, profit))  + facet_wrap(~uncertainty)

@@

``` {r fig.cap="the distribution of profits by scenario", cache=FALSE}
profits <-dt[ , sum(profit), by=c("reps", "uncertainty")] 
ggplot(profits) + geom_histogram(aes(V1)) + facet_wrap(~uncertainty)
````

@@

``` {r, cache=FALSE}
profits[, mean(V1), by=uncertainty]
profits[, sd(V1), by=uncertainty]
````

>>>>

``` {r }
base <- simulatereps(det, 0, 0, 0)
reckless <- simulatereps(det, .2, .2, .2)
````

``` {r }
full <- simulatereps(gmi, .2, .2, .2)
cautious <- simulatereps(gmi, 0, 0, 0)
````

``` {r tidy}
sims <- list(base = base$sims, full = full$sims, reckless=reckless$sims, cautious=cautious$sims)
dat <- melt(sims, id=names(sims[[1]][[1]]))  
dt <- data.table(dat)
setnames(dt, c("L2", "L1"), c("reps", "uncertainty")) # names are nice
````

@@

``` {r  onerep}
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, fishstock)) +
  geom_line(aes(time, harvest), col="darkgreen") + 
  facet_wrap(~uncertainty) 
````

@@

``` {r  fig.cap="the induced dynamics in the stock size over time, for all replicates, by scenario"}
p1 <- ggplot(dt) 
p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1) + facet_wrap(~uncertainty)
````

``` {r fig.cap="The profits made in each time interval of a single replicate, by scenario"}
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, profit))  + facet_wrap(~uncertainty)

@@

``` {r fig.cap="the distribution of profits by scenario"}
profits <-dt[ , sum(profit), by=c("reps", "uncertainty")] 
ggplot(profits) + geom_histogram(aes(V1)) + facet_wrap(~uncertainty)
````

@@

``` {r cache=FALSE}
profits[, mean(V1), by=uncertainty]
profits[, sd(V1), by=uncertainty]
````
